%%%%%%%%%%%%%%%%%
% This is a CV template created using altacv.cls
% (v1.6.4, 13 Nov 2021) written by LianTze Lim (liantze@gmail.com). Now compiles with pdfLaTeX, XeLaTeX and LuaLaTeX.
%
%% It may be distributed and/or modified under the
%% conditions of the LaTeX Project Public License, either version 1.3
%% of this license or (at your option) any later version.
%% The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.3 or later is part of all distributions of LaTeX
%% version 2003/12/01 or later.
%%%%%%%%%%%%%%%%

%% If you need to pass whatever options to xcolor
\PassOptionsToPackage{dvipsnames}{xcolor}

\documentclass[10pt,a4paper,ragged2e,withhyper]{altacv}
%% AltaCV uses the fontawesome5 and packages.
%% See http://texdoc.net/pkg/fontawesome5 for full list of symbols.

% Change the page layout if you need to
\geometry{left=1.25cm,right=1.25cm,top=1.5cm,bottom=1.5cm,columnsep=1.2cm}

% The paracol package lets you typeset columns of text in parallel
\usepackage{paracol}

% Change the font if you want to, depending on whether
% you're using pdflatex or xelatex/lualatex
\ifxetexorluatex
  % If using xelatex or lualatex:
  \setmainfont{Roboto Slab}
  \setsansfont{Lato}
  \renewcommand{\familydefault}{\sfdefault}
\else
  % If using pdflatex:
  \usepackage[rm]{roboto}
  \usepackage[defaultsans]{lato}
  % \usepackage{sourcesanspro}
  \renewcommand{\familydefault}{\sfdefault}
\fi

% Change the colours if you want to
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}
\definecolor{DarkPastelBlue}{HTML}{1E3F66}
\definecolor{PastelBlue}{HTML}{779ECB}
\definecolor{GoldenEarth}{HTML}{E7D192}
\colorlet{name}{black}
\colorlet{tagline}{PastelBlue}
\colorlet{heading}{DarkPastelBlue}
\colorlet{headingrule}{GoldenEarth}
\colorlet{subheading}{PastelBlue}
\colorlet{accent}{PastelBlue}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}

% Change some fonts, if necessary
\renewcommand{\namefont}{\Huge\rmfamily\bfseries}
\renewcommand{\personalinfofont}{\footnotesize}
\renewcommand{\cvsectionfont}{\LARGE\rmfamily\bfseries}
\renewcommand{\cvsubsectionfont}{\large\bfseries}


% Change the bullets for itemize and rating marker
% for \cvskill if you want to
\renewcommand{\cvItemMarker}{{\small\textbullet}}
\renewcommand{\cvRatingMarker}{\faCircle}

%% Use (and optionally edit if necessary) this .cfg if you
%% want to use an author-year reference style like APA(6)
%% for your publication list
\input{pubs-authoryear.cfg}

\begin{document}
\name{Rodolfo Sanchez}
\tagline{Software Engineering Leader}

\personalinfo{%
  \email{me@dolfo.codes}
  \homepage{dolfo.codes}
  \linkedin{dolfolife}
  \github{dolfolife}
}

\begin{fullwidth}
\makecvheader
\end{fullwidth}
\small
Software Engineering Leader with 15+ years building cloud-native platforms. Led Kubernetes and Knative components at VMware
and Pivotal, managed teams of 10+ engineers, and contributed as an open-source maintainer. CKA and CKS certified with expertise in
distributed systems, event-driven architectures, and platform engineering.
\medskip
%% Depending on your tastes, you may want to make fonts of itemized environments slightly smaller
% \AtBeginEnvironment{itemize}{\small}

%% Set the left/right column width ratio to 6:4.
\columnratio{0.5}

% Start a 2-column paracol. Both the left and right columns will automatically
% break across pages if things get too long.
\begin{paracol}{2}

\cvsection{Experience}
\cvevent{}{Senior Software Engineer - Fever}{ Jul 2024 -- Present }{Remote, Spain}
\begin{itemize}
  \item Designed and developed end-to-end ticketing platform serving millions of users and processing 850,000 transactions daily, spanning backend APIs (Python), web clients (Angular), and native mobile applications (Swift/Kotlin).
  \item Mentored junior engineers on system design, code quality, and cloud-native development practices through technical reviews and pair programming sessions.
  \item Partnered with Product, Design, and Mobile teams to deliver customer-facing features with measurable improvements in conversion rates and user satisfaction.
\end{itemize}
\divider
\cvevent{}{Software Engineering Manager - VMware}{ Jan 2020 -- Feb 2024 }{Remote, US}
\begin{itemize}
  \item Owned Eventing Runtime and Function Buildpacks for Kubernetes-based application platform from inception to GA, enabling Tanzu Application Platform applications to reduce lead time for changes and decrease MTTR.
  \item Built and launched DORA metrics observability system across 80 engineering teams, integrating GitHub, CI/CD pipelines, and incident data; surfaced bottlenecks that drove 50\% increase in deployment frequency within 4 quarters.
  \item Grew and developed team of 13 engineers including 3 technical leads; implemented blameless postmortems and incident review processes, reducing Sev-1 incidents by 40\% year-over-year.
  \item Served as maintainer for Knative Eventing and Functions for Knative open-source projects; delivered 2 major releases annually, drove community RFCs, and reviewed 100+ pull requests.
\end{itemize}
\divider

\cvevent{}{Principal Engineer - Software Engineering Manager - Pivotal}{May 2016 -- Dec 2019}{CA, US}
\begin{itemize}
  \item Directed 6-10 engineers responsible for networking components (ingress routers, container-to-container networking) supporting Cloud Foundry platform with 20,000+ applications; achieved 99.999\% uptime SLA with p99 latency under 300--500 ms.
  \item Designed and implemented Kubernetes cluster queue system for testing infrastructure, reducing cluster wait times by 90\% and cutting annual testing infrastructure costs across 80+ teams.
  \item Spearheaded organization-wide Kubernetes adoption program with training sessions for 100+ engineers, accelerating Cloud Foundry to Kubernetes migration and reducing onboarding time by 60\%.
  \item Drove integration of new products into existing Cloud Foundry ecosystem; oversaw migration of legacy monolithic applications to microservices architecture, improving deployment velocity by 70\%+.
  \item Scaled engineering organization from 4 to 80+ engineers across 10+ teams; established practices, code review standards, and CI/CD pipelines that became organizational templates.
\end{itemize}

\divider

\cvevent{}{Sears Holdings, Enova International, and Early Career}{2009 -- 2016}{IL, US}
\begin{itemize}
  \item Advanced from Software Engineer to Lead Developer across multiple organizations, demonstrating consistent growth in technical leadership and system design capabilities.
  \item Supervised 8 engineers building fintech applications processing \$1M+ in transactions daily; established code review standards and coached junior developers on best practices.
  \item Engineered data-intensive e-commerce platform components handling 2M+ daily requests; optimized database queries reducing response times by 40\% and improving overall system performance.
  \item Delivered full-stack web applications and RESTful APIs; gained foundational experience in agile methodologies, software development lifecycle, and production operations.
\end{itemize}

\medskip

%% Switch to the right column. This will now automatically move to the second
%% page if the content is too long.
\switchcolumn

\cvsection{A Day of My Life}

\wheelchart{1.5cm}{0.5cm}{%
  6/8em/accent!40/Strategizing and Planning with Product and Leadership,
  3/8em/accent!30/Learning new technologies and management skills,
  8/8em/accent!60/{Building, Coaching, and mentoring teams},
  1/10em/accent/Coffee,
  5/10em/accent/Coding projects,
  1/6em/accent!20/Spending time with family
}
\cvsection{My Life Philosophy}

\begin{quote}
``Goals, metrics, and knowledge are the foundation to move forward''
\end{quote}

\cvsection{Most Proud of}

\cvachievement{\faTrophy}{Managed 2 Teams Simultaneously}{Successfully balanced leadership of two teams with different objectives, harmonizing varied efforts towards shared organizational goals.}

\divider

\cvachievement{\faHeartbeat}{Team Alignment}{Fostered strong collaboration and efficiency by establishing clear communication channels and ensuring shared vision across all team members.}

\cvsection{Strengths}

\cvtag{Empathetic leadership mindset}
\cvtag{Eye for detail}\\
\cvtag{Motivator \& Leader}

\divider\smallskip

\cvtag{Golang}
\cvtag{JavaScript}
\cvtag{Distributed Systems}\\
\cvtag{Kubernetes}
\cvtag{Serverless}
\cvtag{Cloud Computing}\\
\cvtag{Streaming}
\cvtag{System Design}
\cvtag{Event-Driven Architectures}\\

\medskip


\cvsection{Leadership \& Management}

\cvtag{Team Building}
\cvtag{Coaching}
\cvtag{Mentoring}
\cvtag{Org Design}
\cvtag{Roadmapping}
\cvtag{OKRs}
\cvtag{Cross-functional Alignment}
\cvtag{Stakeholder Management}
\cvtag{Agile/Scrum}
\cvtag{Team Cohesion}
\cvtag{Operational Excellence}

\divider\bigskip

\cvsection{Education \& Certifications}
\cvevent{Certified Kubernetes Administrator (CKA)}{The Linux Foundation}{April 2024 -- April 2027}{}
\cvevent{Certified Kubernetes Security Specialist (CKS)}{The Linux Foundation}{May 2024 -- May 2026}{}
\cvevent{B.Sc.\ in Computer Engineering}{Major on AI and ML}{2005 -- 2010}{Simon Bolivar University}
\end{paracol}

\end{document}
